%--------------------------------Mathematical Oncology----------------------------

\section{Esophageal cancer}

\begin{enumerate}
\item \href{https://www.omim.org/entry/133239?search=Esophageal%20cancer&highlight=%28cancer%7Ccancerous%29%20esophageal}{Esophageal cancer}
\item \href{https://www.malacards.org/card/esophageal_cancer}{Esophageal cancer}
\item \href{https://cancer.sanger.ac.uk/cosmic/search?q=esophageal+cancer}{Esophageal cancer Mutations}
\end{enumerate}

\begin{table}[H]\centering
  \caption {\cite{key400} \cite{480}}
	\begin{tabular}{p{1cm}p{4cm}p{3cm}}
		 MicroRNA & Direction & Relationship & Type\\
		\hline
		miRNA-1 & & & \\
		miRNA-21 & & & \\
		miRNA-23 & & & \\
		miRNA-27a & & & \\
		miRNA-27b & & & \\
		miRNA-28 & & & \\
		miRNA-30 & & & \\
		miRNA-31 & & & \\
		miRNA-99A & & & \\
		miRNA-100 & & & \\
		miRNA-125b & & & \\
		miRNA-133a & & & \\
		miRNA-155 & & & \\
		miRNA-192 & & & \\
		miRNA-194 & & & \\
		miRNA-215 & & & \\
		miRNA-203 & & & \\
		miRNA-205 & & & \\
		miRNA-215 & & & \\
		miRNA-375 & & & \\
		\hline
		miRNA-Let-7 & & & \\
	\end{tabular}
\end{table}




\begin{table}[H]\centering
  \caption {\cite{key450}}
	\begin{tabular}{p{1cm}p{4cm}p{3cm}}
		Chromosome & Gene & Comments\\
		\hline
3p24.1 & TGFBR2 & \\	
8p21.3 &  LZTS1 & \\
13q12.13 & RNF6 & \\	
16q23.1-q23.2 & WWOX & \\ 	
18q21.2 & DCC & \\
		\hline
	\end{tabular}
\end{table}


\section{Clinical Trials}

\href{https://clinicaltrials.gov/ct2/results?cond=Esophageal+cancer&term=&cntry=&state=&city=&dist=}{Esophageal cancer}

\begin{table}[H]\centering
  \caption {\cite{key460}}
	\begin{tabular}{p{1cm}p{4cm}p{3cm}}
		Name & Description & Comments\\
		\hline
		\hline
	\end{tabular}
\end{table}

\section{Genes}

\begin{table}[H]\centering
  \caption {\cite{key400}}
	\begin{tabular}{p{1cm}p{4cm}p{3cm}}
		Gene Name & Change & Comments\\
		\hline
    p53  & mutation & \\
    FAS increased expression & \\
    EGFR & overexpression & \\
    COX2 & overexpression &  \\
    iNOS & increased expression & \\
    Cyclin D1 & amplification & \\
    p16/INK4A & homozygous deletion, LOH & \\
    RB1  & LOH & \\
    APC  & LOH & \\
		\hline
	\end{tabular}
\end{table}

\section{Treatment}

\begin{table}[H]\centering
 \caption {\cite{key470}\cite{key400}}
	\begin{tabular}{p{1cm}p{4cm}p{3cm}}
	Compound & Pubmed Link & Comment\\
		\hline
	Floxuridine & https://pubchem.ncbi.nlm.nih.gov/#query=Floxuridine & Comment\\
	Porfimer sodium & https://pubchem.ncbi.nlm.nih.gov/#query=Porfimer sodium & Comment\\
	\hline
	\end{tabular}
\end{table}



\bibitem[100]{key100} Biological functions of microRNAs: a review.
\bibitem[101]{key101} A Concise Review of MicroRNA Exploring the Insights of MicroRNA Regulations in Bacterial, Viral and Metabolic Diseases.
\bibitem[102]{key102} A brief review on the mechanisms of miRNA regulation



\bibitem[400]{key400} Kanehisa, Furumichi, M., Tanabe, M., Sato, Y., and Morishima, K.; 
\newblock KEGG: new perspectives on genomes, pathways, diseases and drugs. 
\newblock Nucleic Acids Res. 45, D353-D361 (2017).

\bibitem[401]{key401} Kanehisa, M., Sato, Y., Kawashima, M., Furumichi, M., and Tanabe, M.; 
\newblock KEGG as a reference resource for gene and protein annotation. 
\newblock Nucleic Acids Res. 44, D457-D462 (2016).

\bibitem[402]{key402} Kanehisa, M. and Goto, S.; 
\newblock KEGG: Kyoto Encyclopedia of Genes and Genomes. 
\newblock Nucleic Acids Res. 28, 27-30 (2000). 

\bibitem[440]{key440} COSMIC: the Catalogue Of Somatic Mutations In Cancer.

\bibitem[450]{key450} Online Mendelian Inheritance in Man (OMIM), a knowledgebase of human genes and genetic disorders

\bibitem[460]{key460} The ClinicalTrials.gov Results Database — Update and Key Issues

\bibitem[470]{key470} PubChem Substance and Compound databases

\bibitem[480]{key480} The STRING database in 2017: quality-controlled protein–protein association networks, made broadly accessible

\bibitem[490]{key490} MalaCards: an amalgamated human disease compendium with diverse clinical and genetic annotation and structured search


