%-----------------------------------------Cell Signal Transduction Networks------------------------

\section{ErbB-EGFR}

\begin{enumerate}
\item \href{https://www.genome.jp/kegg-bin/show_pathway?map=hsa04012&show_description=show}{ERBB}

\end{enumerate}

\section{Equation System}

d.1.EGFR.dt.1 
d.1.SHC2.dt.1 
d.1.PLCG1.dt.1 
d.1.STAT5A.dt.1 
d.1.CRK.dt.1 
d.1.SRC.dt.1 
d.1.GRB2.dt.1  


\section{Molecular Annotations and Document Compendium}

Table 1 shows the list of molecular species for the network
\vspace{8pt}
\begin{table}[H]
	\begin{tabular}{rlllll}
		\hline
		ID & Gene & Variable & Description & Activation \\ 
		\hline
		\href{https://www.malacards.org/search/results/CBL}{\textbf{CBL}} & CBL & $x_1$ & & \\
		\href{https://www.malacards.org/search/results/TB53}{\textbf{TP53}} & TP53 & $x_2$ & & \\
		\href{https://www.malacards.org/search/results/GRB2}{\textbf{GRB2}} & GRB2 & $x_3$ & & \\
		\href{https://www.malacards.org/search/results/PTPN11}{\textbf{PTPN11}} & PTPN11 & $x_4$ & & \\ 
		\href{https://www.malacards.org/search/results/KRAS}{\textbf{KRAS}} & KRAS & $x_5$ & & \\
		\href{https://www.malacards.org/search/results/SHC1}{\textbf{SHC1}} & SHC1 & $x_6$ & & \\
		\href{https://www.malacards.org/search/results/PIK3CA}{\textbf{PIK3CA}} & PIK3CA & $x_7$ & & \\ 
		\href{https://www.malacards.org/search/results/HRAS}{\textbf{HRAS}} & HRAS & $x_8$ & & \\
		\href{https://www.malacards.org/search/results/ERBB3}{\textbf{ERBB3}} & ERBB3 & $x_9$ & & \\
		\href{https://www.malacards.org/search/results/EGF}{\textbf{EGF}} & EGF & $x_{10}$ & & \\
		\href{https://www.malacards.org/search/results/EGFR}{\textbf{EGFR}} & EGFR & $x_{11}$ & & \\
		\href{https://www.malacards.org/search/results/TGFA}{\textbf{TGFA}} & TGFA & $x_{12}$ & & \\
		\hline
	\end{tabular}
	\caption{Network}
	\label{tab:Table2}
\end{table}



\bibitem[100]{key100} Epidermal growth factor receptor (EGFR) tyrosine kinase inhibitors in non-small cell lung cancer harboring uncommon EGFR mutations: Focus on afatinib.
\bibitem[101]{key101} Clinical management of third-generation EGFR inhibitor-resistant patients with advanced non-small cell lung cancer: Current status and future perspectives.
\bibitem[102]{key102} EGFR inhibitors as adjuvant therapy for resected non-small cell lung cancer harboring EGFR mutations.
\bibitem[103]{key103} A meta-analysis of adjuvant EGFR-TKIs for patients with resected non-small cell lung cancer.


\bibitem[400]{key400} Kanehisa, Furumichi, M., Tanabe, M., Sato, Y., and Morishima, K.; 
\newblock KEGG: new perspectives on genomes, pathways, diseases and drugs. 
\newblock Nucleic Acids Res. 45, D353-D361 (2017).

\bibitem[401]{key401} Kanehisa, M., Sato, Y., Kawashima, M., Furumichi, M., and Tanabe, M.; 
\newblock KEGG as a reference resource for gene and protein annotation. 
\newblock Nucleic Acids Res. 44, D457-D462 (2016).

\bibitem[402]{key402} Kanehisa, M. and Goto, S.; 
\newblock KEGG: Kyoto Encyclopedia of Genes and Genomes. 
\newblock Nucleic Acids Res. 28, 27-30 (2000).

\bibitem[420]{key420}GeneCards Version 3: the human gene integrator

\bibitem[430]{key430} DrugBank 5.0: a major update to the DrugBank database for 2018.

\bibitem[440]{key440} COSMIC: the Catalogue Of Somatic Mutations In Cancer.

\bibitem[450]{key450} Online Mendelian Inheritance in Man (OMIM), a knowledgebase of human genes and genetic disorders

\bibitem[460]{key460} The ClinicalTrials.gov Results Database — Update and Key Issues

\bibitem[470]{key470} PubChem Substance and Compound databases

\bibitem[480]{key480} The STRING database in 2017: quality-controlled protein–protein association networks, made broadly accessible

\bibitem[490]{key490} MalaCards: an amalgamated human disease compendium with diverse clinical and genetic annotation and structured search
