%-----------------------------------------Cell Signal Transduction Networks------------------------
\section{RAS}

\section{Genes}

\begin{table}[H]\centering
  \caption {\cite{key400}}
	\begin{tabular}{p{1cm}p{4cm}p{3cm}}
		Gene Name & Activity Change & Comments\\
		\hline
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]\centering
  \caption {\cite{key400} \cite{480}}
	\begin{tabular}{p{1cm}p{4cm}p{3cm}}
		 Gene A & Gene B & Relationship & Reference\\
		\hline
\end{tabular}
\end{table}


\section{Clinical Trials}

begin{table}[H]\centering
  \caption {\cite{key460}}
	\begin{tabular}{p{1cm}p{4cm}p{3cm}}
		Name & Description & Comments\\
		\hline
		\hline
	\end{tabular}
\end{table}


\section{Treatment}

\begin{table}[H]\centering
 \caption {\cite{key470}\cite{key400}}
	\begin{tabular}{p{1cm}p{4cm}p{3cm}}
	Compound & Link 1 & Reference\\
		\hline

\hline
	\end{tabular}
\end{table}




 
\bibitem[100]{key100} Overview of the oncogenic signaling pathways in colorectal cancer: Mechanistic insights.
\bibitem[101]{key101}Oncogenic Mutations Rewire Signaling Pathways by Switching
\bibitem[102]{key102} Screening common signaling pathways associated with drug resistance in non-small cell lung cancer via gene expression profile analysis. Protein Recruitment to Phosphotyrosine Sites
\bibitem[103]{key103} Notch and mTOR Signaling Pathways Promote Human Gastric Cancer Cell Proliferation.
\bibitem[104]{key104} The Signaling Pathways Project, an integrated ‘omics knowledgebase for mammalian cellular signaling pathways
\bibitem[105]{key105} The signaling pathways that mediate the anti-cancer effects of caloric restriction.
\bibitem[106]{key106} Mitochondria in the signaling pathways that control longevity and health span.


\bibitem[400]{key400} Kanehisa, Furumichi, M., Tanabe, M., Sato, Y., and Morishima, K.; 
\newblock KEGG: new perspectives on genomes, pathways, diseases and drugs. 
\newblock Nucleic Acids Res. 45, D353-D361 (2017).

\bibitem[401]{key401} Kanehisa, M., Sato, Y., Kawashima, M., Furumichi, M., and Tanabe, M.; 
\newblock KEGG as a reference resource for gene and protein annotation. 
\newblock Nucleic Acids Res. 44, D457-D462 (2016).

\bibitem[402]{key402} Kanehisa, M. and Goto, S.; 
\newblock KEGG: Kyoto Encyclopedia of Genes and Genomes. 
\newblock Nucleic Acids Res. 28, 27-30 (2000).

\bibitem[420]{key420}GeneCards Version 3: the human gene integrator

\bibitem[430]{key430} DrugBank 5.0: a major update to the DrugBank database for 2018.

\bibitem[440]{key440} COSMIC: the Catalogue Of Somatic Mutations In Cancer.

\bibitem[450]{key450} Online Mendelian Inheritance in Man (OMIM), a knowledgebase of human genes and genetic disorders

\bibitem[460]{key460} The ClinicalTrials.gov Results Database — Update and Key Issues

\bibitem[470]{key470} PubChem Substance and Compound databases

\bibitem[480]{key480} The STRING database in 2017: quality-controlled protein–protein association networks, made broadly accessible

\bibitem[490]{key490} MalaCards: an amalgamated human disease compendium with diverse clinical and genetic annotation and structured search
