%-----------------------------------------Cell Signal Transduction Networks------------------------
%-----------------------------------------Work in Progress-----------------------------------------

\section{Chemokine}

\begin{enumerate}
\item \href{https://www.genome.jp/kegg-bin/show_pathway?map=hsa04012&show_description=show}{Chemokine}
\end{enumerate}

\section{Equation System}


\begin{table}[H]
	\tiny
	\begin{tabular}{p{1cm}p{1cm}p{3cm}p{1cm}p{1cm}} 
		EdgeID & Gene 1 & Gene 2 & Biological Function & Comment \\
		\hline
    
    \end{tabular}
	\caption{Chemokine Network}
	\label{tab:Table2}
\end{table}


\section{Molecular Annotations and Document Compendium}

Table 1 shows the list of molecular species for the network
\vspace{8pt}
\begin{table}[H]
	\begin{tabular}{rlllll}
		\hline
		ID & Gene & Variable & Description & Activation \\ 
		\hline

		\hline
	\end{tabular}
	\caption{Network}
	\label{tab:Table2}
\end{table}

\section{Bibliography}

\bibliographystyle{plain}
\begin{thebibliography}{00}


\bibitem[400]{key400} Kanehisa, Furumichi, M., Tanabe, M., Sato, Y., and Morishima, K.; 
\newblock KEGG: new perspectives on genomes, pathways, diseases and drugs. 
\newblock Nucleic Acids Res. 45, D353-D361 (2017).
\bibitem[401]{key401} Kanehisa, M., Sato, Y., Kawashima, M., Furumichi, M., and Tanabe, M.; 
\newblock KEGG as a reference resource for gene and protein annotation. 
\newblock Nucleic Acids Res. 44, D457-D462 (2016).
\bibitem[402]{key402} Kanehisa, M. and Goto, S.; 
\newblock KEGG: Kyoto Encyclopedia of Genes and Genomes. 
\newblock Nucleic Acids Res. 28, 27-30 (2000).


\bibitem[420]{key420}GeneCards Version 3: the human gene integrator

\bibitem[430]{key430} DrugBank 5.0: a major update to the DrugBank database for 2018.

\bibitem[440]{key440} COSMIC: the Catalogue Of Somatic Mutations In Cancer.

\bibitem[450]{key450} Online Mendelian Inheritance in Man (OMIM), a knowledgebase of human genes and genetic disorders

\bibitem[460]{key460} The ClinicalTrials.gov Results Database — Update and Key Issues

\bibitem[470]{key470} PubChem Substance and Compound databases

\bibitem[480]{key480} The STRING database in 2017: quality-controlled protein–protein association networks, made broadly accessible

\bibitem[490]{key490} MalaCards: an amalgamated human disease compendium with diverse clinical and genetic annotation and structured search

\end{thebibliography}
\end{document}
