%-------------------------------------------------------------------------%
%--------------------Classroom Lecture Model Series-----------------------%
%-------------------------------------------------------------------------%

\begin{document}
\twocolumn
\scriptsize
\begin{frontmatter}
		\title{}
		\author{\corref{cor1}\fnref{fn1}}
		\cortext[cor1]{Corresponding author}
		\address{The Mathematical Learning Space}
		\ead{http://mathlearningspace.weebly.com}	
\end{frontmatter}	

Introduction:
\begin{enumerate}
\item Objective 1:
\item Objective 2:
\item Objective 3:
\end{enumerate}
Conclusion:

Keywords:  Molecular Machine Learning, Shikimate Pathway, Mathematical chemistry, QSAR, Topological index,Docking (molecular), secondary  metabolites
Vocabulary Words: phenylpropanoids, phytochemicals

\section{Introduction}


\subsection{Plan of the Article}

\section{Topic Review: Mathenmatical Chemistry}

\subsection{Phenylpropanoid Pathway}


\subsection{Plant BioChemistry and Phytochemistry Background}


\section{Conclusions}


\section{R Application Programming Interfaces (APIs)}




\bibliographystyle{plain}
\begin{thebibliography}{00}

\bibitem[1]{key1}N. Trinajstić, I. Gutman, 
\newblock Mathematical Chemistry, 
\newblock Croatica Chemica Acta, 75(2002), pp. 329–356.

\bibitem[2]{key2}A. T. Balaban, 
\newblock Reflections about Mathematical Chemistry, 
\newblock Foundations of Chemistry, 7(2005), pp. 289–306.

\bibitem[3]{key3}G. Restrepo, J. L. Villaveces, 
\newblock Mathematical Thinking in Chemistry, HYLE, 18(2012), pp. 3–22.
\newblock Advances in Mathematical Chemistry and Applications. Volume 2. Basak S. C., Restrepo G., Villaveces J. L. (Bentham Science eBooks, 2015)

\bibitem[100]{key100}Brian Maitner (2018). 
\newblock BIEN: Tools for Accessing the Botanical Information and Ecology
\newblock Network Database. R package version 1.2.3. https://CRAN.R-project.org/package=BIEN

\bibitem[101]{key101} Paradis E., Claude J. and Strimmer K. 2004. 
\newblock APE: analyses of phylogenetics and evolution in R language. 
\newblock Bioinformatics 20: 289-290.

\bibitem[301]{key301} Klaus M. Herrmann 
\newblock The Shikimate Pathway as an  Entry to Aromatic Secondary Metabolism' 
\newblock Plant Physiol. (1995) 107: 7-12

\bibitem[302]{key302} Wikipedia contributors. 
\newblock Shikimate pathway 
\newblock Wikipedia, The Free Encyclopedia. Wikipedia. 

\bibitem[303]{key303}Wikipedia contributors. 
\newblock "Watercress." 
\newblock Wikipedia, The Free Encyclopedia. 

\bibitem[304]{key304} Voutsina et al.
\newblock Characterization of the watercress(Nasturtium officinaleR. Br.; Brassicaceae) transcriptome using RNASeq and
identification of candidate genes for important phytonutrient traits linked to human health
\newblock BMC Genomics (2016) 17:378 

\bibitem[401]{key401} 
\newblock Functional Foods 
\newblock Health and Disease 2012, 2(11):460-48

\bibitem[1000]{key1000}R Core Team (2015). 
\newblock R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria.
\newblock URL https://www.R-project.org/.

\end{thebibliography}
\end{document}
