%-------------------------------------------------------------------------%
%--------------------Classroom Lecture Model Series-----------------------%
%-------------------------------------------------------------------------%

\begin{document}
\twocolumn
\scriptsize
\begin{frontmatter}
		\title{}
		\author{\corref{cor1}\fnref{fn1}}
		\cortext[cor1]{Corresponding author}
		\address{The Mathematical Learning Space}
		\ead{http://mathlearningspace.weebly.com}	
\end{frontmatter}	

Introduction:
\begin{enumerate}
\item Objective 1:
\item Objective 2:
\item Objective 3:
\end{enumerate}
Conclusion:

Keywords: Stochastic Differential Equations, Bayesian Markov Chain Monte Carlo, Gene Ontology, VEGFC, Lymphangiogenesis
Vocabulary Words:

\section{Introduction}

\subsection{Plan of the Article}


\section{Topic Review}

\begin{table}[H]
\centering
\begin{tabular}{r|p{12cm}|l}
\hline
PubmedID  & Title & Summary \\
\hline	
\hline
	\end{tabular}
	\caption{Summary of Literature Review for Topic}
\end{table}		

\subsection{GO: Biological Process}

\subsection{GO: Molecular Function}

\subsection{GO: Cellular Component}

\section{Mathematical Background}

\subsection{Bayesian inference}

\subsubsection{Uniform Distribution}

\subsubsection{Normal, Beta, and Gamma Distributions}

\subsection{Bayesian MCMC}

\section{Equation Systems}

\subsection{Drift and Diffusion Parameter Specifications}

\subsection{Error Term Specifications}

\section{Results}

\subsection{Tables}

\subsection{Figures}


\section{Conclusions}


\section{R Application Programming Interfaces (APIs)}


\bibliographystyle{plain}
\begin{thebibliography}{00}
		
\bibitem[101]{key101}Yoshida, N. (2011). 
\newblock Polynomial type large deviation inequalities and quasi-likelihood analysis for stochastic differential equations. 
\newblock Annals of the Institute of Statistical Mathematics, 63(3), 431-479.

\bibitem[102]{key102}Uchida, M., and Yoshida, N. (2014). 
\newblock Adaptive Bayes type estimators of ergodic diffusion processes from discrete observations. 
\newblock Statistical Inference for Stochastic Processes, 17(2), 181-219.

\bibitem[103]{key103}Kamatani, K. (2017).
\newblock Ergodicity of Markov chain Monte Carlo with reversible proposal. 
\newblock Journal of Applied Probability, 54(2).
	
\bibitem[104]{key104}Barndorff-Nielsen, O. E. and Shephard, N. (2004) 
\newblock Power and bipower variation with stochastic volatility and jumps, 
\newblock Journal of Financial Econometrics, 2, no. 1, 1–37.
	
\bibitem[105]{key105}Barndorff-Nielsen, O. E. and Shephard, N. (2006) 
\newblock Econometrics of testing for jumps in financial economics using bipower variation, 
\newblock Journal of Financial Econometrics, 4, no. 1, 1–30.
	
\bibitem[106]{key106}Huang, X. and Tauchen, G. (2005) 
\newblock The relative contribution of jumps to total price variance, 
\newblock Journal of Financial Econometrics, 3, no. 4, 456–499.
	
\end{thebibliography}
\end{document}
