%-------------------------------------------------------------------------%
%--------------------Classroom Lecture Model Series-----------------------%
%-------------------------------------------------------------------------%

\begin{document}
\twocolumn
\scriptsize
\begin{frontmatter}
		\title{}
		\author{\corref{cor1}\fnref{fn1}}
		\cortext[cor1]{Corresponding author}
		\address{The Mathematical Learning Space}
		\ead{http://mathlearningspace.weebly.com}	
\end{frontmatter}	

Introduction:
\begin{enumerate}
\item Objective 1:
\item Objective 2:
\item Objective 3:
\end{enumerate}
Conclusion:

Keywords: KEGG Database, NCI-60 Cell lines, Gene Ontology, NCI Ontology
Vocabulary Words:

\section{Introduction}

\subsection{Plan of the Article}


\section{Topic Review}

\subsection{Topic A: KEGG Database}

\subsection{Topic B: NCI- 60 Cell Lines}

\subsection{Topic C: Gene Ontology}

\subsection{Topic D: NCI Ontology}

\subsection{Diagram}

\section{Mathematical Model}

\subsection{Equations}

\subsection{Parameter Table}

\begin{table}[H]\centering
\begin{tabular}{p{1cm}p{1cm}p{1cm}p{1cm}p{1cm}p{1cm}p{4cm}}\
Parameter & Name & Value & Interval & PDF & Sample & Reference \\
\hline
\hline
\end{tabular}
\end{table}

\section{Methods}

\subsection{Algorithms}

\section{Results}

\subsection{Tables}

\subsection{Figures}

\subsection{Classroom Discussion}

\section{Bibliography}

\bibliographystyle{plain}
\begin{thebibliography}{00}

\bibitem[1]{key1}Arwen Meister, Ye Henry Li, Bokyung Choi and Wing Hung Wong
\newblock Learning A Nonlinear Dynamical System Model Of Gene Regulation: A Perturbed Steady-State Approach
\newblock The Annals of Applied Statistics 2013, Vol. 7, No. 3, 1311–1333.

\bibitem[2]{key2}H. Frederik Nijhout, Janet A. Best and Michael C. Reed
\newblock Using mathematical models to understand metabolism, genes, and disease
\newblock BMC Biology (2015) 13:79.

\bibitem[400]{key400} Kanehisa, Furumichi, M., Tanabe, M., Sato, Y., and Morishima, K.; 
\newblock KEGG: new perspectives on genomes, pathways, diseases and drugs. 
\newblock Nucleic Acids Res. 45, D353-D361 (2017).

\bibitem[401]{key401} Kanehisa, M., Sato, Y., Kawashima, M., Furumichi, M., and Tanabe, M.; 
\newblock KEGG as a reference resource for gene and protein annotation. 
\newblock Nucleic Acids Res. 44, D457-D462 (2016).

\bibitem[402]{key402} Kanehisa, M. and Goto, S.; 
\newblock KEGG: Kyoto Encyclopedia of Genes and Genomes. 
\newblock Nucleic Acids Res. 28, 27-30 (2000). 

\bibitem[403]{key403} Rouillard AD, Gundersen GW, Fernandez NF, Wang Z, Monteiro CD, McDermott MG, Ma'ayan A. 
\newblock The harmonizome: a collection of processed datasets gathered to serve and mine knowledge about genes and proteins. 
\newblock Database (Oxford). 2016 Jul 3;2016. pii: baw100. 

\bibitem[1000]{key1000}R Core Team (2015). 
\newblock R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria.
\newblock URL https://www.R-project.org/.

\end{thebibliography}

\end{document}
