
\bibliographystyle{plain}
\begin{thebibliography}{00}
\small

\section{Main Articles for Classroom Lecture Designs in November 2018}
 
\bibitem[1]{key100}Philip S. Crooke and Fritz F. Parl
\newblock A Mathematical Model for DNA Damage and Repair
\newblock Journal of Nucleic Acids Volume 2010, Article ID 352603, 7 pages

\bibitem[2]{key101} G.D. Farquhar, S. von Caemmerer and J.A. Berry  
\newblock A Biochemical Model of Photosynthetic CO 2 Assimilation in Leaves of C 3 Species 
\newblock Planta 149, 78-90 (1980) 

\bibitem[3]{key102} Wikipedia contributors. 
\newblock "Magnesium." 
\newblock Wikipedia, The Free Encyclopedia. Wikipedia, The Free Encyclopedia, 21 Oct. 2018. Web. 29 Oct. 2018. 

\bibitem[4]{key103}Wikipedia contributors. 
\newblock "Generalized logistic distribution." 
\newblock Wikipedia, The Free Encyclopedia. Wikipedia, The Free Encyclopedia, 10 Jun. 2017. Web. 29 Oct. 2018. 

\bibitem[5]{key104}Sahattaya Rattanamongkonkul,  Wannapa Kunpasuruang, Sittipong Ruktamatakul and Chontita Rattanaku
\newblock A Mathematical Model of Bone Remodeling Process:  Effect of Vitamin D
\newblock INTERNATIONAL JOURNAL OF MATHEMATICS AND COMPUTERS IN SIMULATION

\bibitem[6]{key105}Nigar Ali GulZaman and Obaid Algahtan
\newblock Stability analysis of HIV-1 model with multiple delays
\newblock Advances in Difference Equations (2016) 2016:88 

\bibitem[7]{key106} Luca Gori,Luca Guerrini,and Mauro Sodini
\newblock Hopf Bifurcation in a Cobweb Model with Discrete Time Delays
\newblock Discrete Dynamics in Nature and Society Volume 2014, Article ID 137090, 8 pages http://dx.doi.org/10.1155/2014/13709

\bibitem[8]{key107} Christian Beck, Sebastian Becker, Philipp Grohs, Nor Jaafari, and Arnulf Jentzen
\newblock Solving stochastic differential equations and Kolmogorov equations by means of deep learning\section{Topoisomerase (DNA) I}

\section{Topoisomerase (DNA) I}

\bibitem[1]{key3000}Gellert M.
\newblock DNA topoisomerases.
\newblock Annu Rev Biochem 50:879-910 (1981) DOI:10.1146/annurev.bi.50.070181.004311

\section{Topoisomerase (DNA) II}

\bibitem[1]{key3001}Nitiss, J. L. (2009). 
\newblock Targeting DNA topoisomerase II in cancer chemotherapy. Nature Reviews. 
\newblock Cancer, 9(5), 338–350. http://doi.org/10.1038/nrc2607


\section{Antineoplastic}

\bibitem[1]{key2000}Gordon M Cragg and David J Newman (2000) 
\newblock Antineoplastic agents from natural sources: achievements and future directions, 
\newblock Expert Opinion on Investigational Drugs, 9:12, 2783-2797, DOI: 10.1517/13543784.9.12.2783

\bibitem[2]{key2001}Varricchi, Gilda and Ameri, Pietro and Cadeddu, Christian and Ghigo, Alessandra and Madonna, Rosalinda and Marone, Giancarlo and Mercurio, Valentina and Monte, Ines and Novo, Giuseppina and Parrella, Paolo and Pirozzi, Flora and Pecoraro, Antonio and Spallarossa, Paolo and Zito, Concetta and Mercuro, Giuseppe and Pagliaro, Pasquale and Tocchetti, Carlo G. (2018)  
\newblock Antineoplastic Drug-Induced Cardiotoxicity: A Redox Perspective 
\newblock Frontiers in Physiology 9 : 167  https://www.frontiersin.org/article/10.3389/fphys.2018.00167 10.3389/fphys.2018.00167

\bibitem[3]{key2002}Sheng, Jianting and Li, Fuhai and Wong, Stephen (2015)
\newblock Optimal Drug Prediction From Personal Genomics Profiles
\newblock IEEE journal of biomedical and health informatics 19

\bibitem[4]{key2003} Chayaporn Suphavilai, Denis Bertrand, Niranjan Nagarajan; 
\newblock Predicting Cancer Drug Response using a Recommender System, 
\newblock Bioinformatics, , bty452, https://doi.org/10.1093/bioinformatics/bty452

\bibitem[5]{key2004}Foster, A. E., and Reeves, D. J. (2017). 
\newblock Inpatient Antineoplastic Medication Administration And Associated Drug Costs: Institution of a Hospital Policy Limiting Inpatient Administration. 
\newblock Pharmacy and Therapeutics, 42(6), 388–393.

\section{Pharmaceutical Portfolio}

\bibitem[1]{key400} Christian Garavaglia, Franco Malerba, Luigi Orsenigo, Michele Pezzoni
\newblock Innovation and Market Structure in Pharmaceuticals An Econometric Analysis on Simulated Data
\newblock Jahrbücher für Nationalökonomie und Statistik April 2014

\bibitem[2]{key401} http://www.worldpharmanews.com/research-and-development

\section{Wikipedia}

\bibitem[1]{key8000} Shafee T, Masukume G, Kipersztok L, et al
\newblock Evolution of Wikipedia’s medical content: past, present and future
\newblock J Epidemiol Community Health 2017;71:1122-1129.


\end{thebibliography}
\end{document}
